The \kplr\ Catalog: Systematic probabilistic parameter estimation for every \kepler\ planet candidate

### 2013-12-26 document/ms.tex
description of model and parameters

@@

A model, from our perspective,
is a parameterized probability for the data,
and a prior probability distribution over parameters.
For the probability of the data, we do [XXX chi-squared].

>>>>

TODO: Talk about the philosophy of interim priors here.

TODO: Justify the use of non-physically motivated parameters and relate this
to the idea of sufficient statistics.

@@

A model, from our perspective, is a parameterized probability for the data,
the likelihood function, and a prior probability distribution over parameters.
We will also divide the likelihood further into a \emph{deterministic physical
generative model} and a \emph{stochastic noise model}.
The form for each of these model components can be freely chosen and in the
next sections, we'll justify our specific choices.
In short, we assume independent Gaussian noise, a Mandel \& Agol (CITE) like
limb darkened light curve, and simple interim priors.

\paragraph{Noise model}
The noise in the light curves generated by the Kepler pipeline result from a
large collection of effects.
There are both astrophysical sources (stellar variability, \etc) instrumental
effects (photon noise, temperature and pointing variations, \etc).
The exact effect of each of these effects is complicated by the aperture
photometry procedure and all of the preconditioning steps discussed above.
Despite these complications, we'll assume that the error bars produced by the
Kepler pipeline are good estimates and that they are distributed independently
and normally.
This is a reasonable assumption because TODO.

\paragraph{Generative model}
For this project, we assume a quadratic limb darkened light curve model
following Mandel \& Agol (CITE) and integrate over exposure time (Kipping
CITE, Appendix XXXX).
Since we don't want to be dependent on specific stellar parameters and since
we would like to make it easy to apply any new stellar catalogs, we don't use
physical orbits.
Instead, we parameterize the orbit using only ``observable'' parameters.
In particular, we use, for the star, the mean stellar flux \fstar, and the
parameters \qone\ and \qtwo\ of a quadratic limb darkening profile
(parameterized following Kipping CITE).
For each companion, we parameterize the orbit using period \period, epoch
\epoch, transit duration \duration, radius ratio \ror, and impact parameter
\impact.

\paragraph{Interim priors}
For simplicity---and that is the main goal when using interim priors---we
chose to model the prior probabilities for each parameter as uniform
distributions in the linear parameter except the radius ratio.
For this distribution, we use
\begin{eqnarray}
p(\ror) &\propto& \left \{ \begin{array}{ll}
1/\ror^2 & \ror_\mathrm{min} \le \ror \le 1 \\
0 & \mathrm{otherwise} \\
\end{array}\right.
\end{eqnarray}
where we conservatively choose $\ror_\mathrm{min} = 10^{-4}$.

\begin{deluxetable}{lclcc}
\tabletypesize{\footnotesize}
\tablecolumns{3}
\tablewidth{0pt}

\tablecaption{%
The parameters of the generative model and their associated interim priors.
\tablabel{parameters}}

\tablehead{%
\colhead{Symbol} &
\colhead{Unit} &
\colhead{Description} &
\colhead{Range} &
\colhead{Prior}
}

\startdata

\fstar & --- & mean stellar flux & $[0, 2]$ & Uniform \\
\qone & --- & first limb darkening coefficient & $[0, 1]$ & Uniform \\
\vspace{0.5cm}
\qtwo & --- & second limb darkening coefficient & $[0, 1]$ & Uniform \\

\period & days & orbital period & $[0, 1000]$\tablenotemark{a} & Uniform \\
\epoch & days & center time of reference transit & $[0, 1000]$\tablenotemark{a}
       & Uniform \\
\duration & days & transit duration\tablenotemark{b} & $[0, 10]$ & Uniform \\
\ror & --- & radius ratio & $[10^{-4}, 1]$ & $1/\ror^2$ \\
\impact & --- & impact parameter & $[0, 2]$ & Uniform \\

\enddata

\tablenotetext{a}{%
In practice, we use more constraining priors on \period\ and \epoch\
because the initial values are very close to correct in most cases but this
doesn't affect the results.
}
\tablenotetext{b}{%
The transit duration is defined as the time between initial contact and
final contact.
}
\end{deluxetable}

For the probability of the data, we do [XXX chi-squared].
